Report

### 2019-05-09 index.Rmd
a few comments were updated

Isomap is a three steps procedure that takes as input a set of points $x_1,\ldots,x_n\in \R^D$ and produces an embedding of the input data in the space $\R^d$ with $d<D$, that preserves pairwise geodesic distances. The first step consists in constructing a weighted graph $G$ with nodes corresponding to the input data and for which the weight of an edge between two nodes $x_i$ and $x_j$ is equal to $||x_i-x_j ||_{\R^D}$. The graph $G$ is constructed such that a node is connected to a fix number $N$ of neighbors or to all nodes that are at a distance smaller than a given value $\epsilon$. In the second step, the pairwise geodesic distances $d_\M(x_i,x_j)$
are estimated based on $G$. The geodesic distance between two nodes is simply the length of the shortest path in $G$ between these two nodes, and can be calculated easily with Floyd-Warshall or Dijkstra’s algorithms. The last step consists in using MDS on the matrix of pairwise geodesic distances obtained in the first step in order to obtain an embedding in $\R^d$.

@@

* Clean up the writing in this notebook. Add code and graphs where helpful.
* Related to tuning parameter
    + Choose the number of neighbors $N$ in IsoGeo.
    + Choose projection dimension for avoiding curse of dimensionality in performing density ridge scms routine
    + Choose the bandwidth $h$ in scms.
* Related to spartanSim.R simulations results
    + Why do some Monte Carlo simulations fail?
    + Is P-isomap always choosing zero penalty automatically?
    + Shouldn’t the smoothing method be doing better? Thought the smooth was close to the true curve.
* Next time we submit spartanSim.R, make sure to hold dataset constant for different projection dimensions
* Read Marie's suggested paper on robust ISOMAP
* Revisit Mueller manifold examples. Need to write down some differential equations to solve the geodesic minimisation problem?

>>>>

Isomap is a three steps procedure that takes as input a set of points $x_1,\ldots,x_n\in \R^D$ and produces an embedding of the input data in the space $\R^d$ with $d<D$, that preserves pairwise geodesic distances. The first step consists in constructing a weighted graph $G$ with nodes corresponding to the input data and for which the weight of an edge between two nodes $x_i$ and $x_j$ is equal to $||x_i-x_j ||_{\R^D}$. The graph $G$ is constructed such that a node is connected to a fix number $N$ of neighbors or to all nodes that are at a distance smaller than a given value $\epsilon$. In the second step, the pairwise geodesic distances $d_\M(x_i,x_j)$
are estimated based on $G$. The geodesic distance between two nodes is simply the length of the shortest path in $G$ between these two nodes, and can be calculated easily with Floyd-Warshall or Dijkstra’s algorithms. The last step consists in using MDS on the matrix of pairwise geodesic distances obtained in the first step in order to obtain an embedding in $\R^d$. 
```{r}
3 + 5
```

@@

* Clean up the writing in this notebook. Add code and graphs where helpful.
* Related to tuning parameter
    + Choose the number of neighbors $N$ in IsoGeo.
    + Choose projection dimension for avoiding curse of dimensionality in performing density ridge scms routine
    + Choose the bandwidth $h$ in scms.
* Related to spartanSim.R simulations results
    + Why do some Monte Carlo simulations fail?
    + Is P-isomap always choosing zero penalty automatically?
    + Shouldn’t the smoothing method be doing better? Thought the smooth was close to the true curve.
* Next time we submit spartanSim.R, make sure to hold dataset constant for different projection dimensions
* Read Marie's suggested paper on [robust ISOMAP](https://arxiv.org/abs/1306.3373)
* Revisit Mueller manifold examples. Need to write down some differential equations to solve the geodesic minimisation problem?
